Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-01-23 README.Rmd
update README

1.  [`Manuscript`](https://stefanvermeent.github.io/abcd_ddm/registered_report/README.html): The Registered Report written in Quarto.
2.  [`Supplement`](https://stefanvermeent.github.io/abcd_ddm/supplement/README.html): a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
3.  [`Scripts`](https://stefanvermeent.github.io/abcd_ddm/scripts/README.html): R-scripts that read, analyze, and produce all analysis objects.
4.  [`Data`](https://stefanvermeent.github.io/abcd_ddm/data/README.html): Folder in which real LISS data can be placed to make the analyses fully reproducible. Note that we cannot openly share the raw data on the open repository. The folder contains synthetic data to facilitate computational reproducibility in the absence of LISS access.
5.  [`Analysis Objects`](https://stefanvermeent.github.io/abcd_ddm/analysis_objects/README.html): Folder containing all analysis objects.
6.  [`Codebooks`](https://stefanvermeent.github.io/abcd_ddm/codebooks/README.html): lists of variable names, labels, and value labels (where applicable).

>>>>

1.  [`Manuscript`](https://stefanvermeent.github.io/liss_wm_profiles_2023/manuscript/README.html): The Registered Report written in Quarto.
2.  [`Supplement`](https://stefanvermeent.github.io/liss_wm_profiles_2023/supplement/README.html): a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
3.  [`Scripts`](https://stefanvermeent.github.io/liss_wm_profiles_2023/scripts/README.html): R-scripts that read, analyze, and produce all analysis objects.
4.  [`Materials`](https://stefanvermeent.github.io/liss_wm_profiles_2023/materials/README.html): JsPsych scripts of the Working Memory tasks.
4.  [`Data`](https://stefanvermeent.github.io/liss_wm_profiles_2023/data/README.html): Folder in which real LISS data can be placed to make the analyses fully reproducible. Note that we cannot openly share the raw data on the open repository. The folder contains simulated data to facilitate computational reproducibility in the absence of LISS access.
5.  [`Analysis Objects`](https://stefanvermeent.github.io/liss_wm_profiles_2023/analysis_objects/README.html): Folder containing all analysis objects (as produced by the analysis scripts).
6.  [`Codebooks`](https://stefanvermeent.github.io/liss_wm_profiles_2023/codebooks/README.html): lists of variable names, labels, and value labels (where applicable).
